Efficient Coalition Formation for Web Services

### 2013-03-11 papers/coalition/coalition.tex
Changes

In this scenario we consider multiple communities owned by multiple master web services which provide independent request pools. Like first scenario master web services form coalitions with web services. We use coalition structure formation methods to partition web services into non-empty disjoint coalition structures. As mentioned in section \ref{sec:coalition} these algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve two fundamental problems of what coalitions to form, and how will the members of these coalitions distribute their total gain to make these coalition structures stable.

@@

The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has two or more master web services as members.

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions. 
This merge-and-split algorithm is designed to be adoptable for different problems. It requires two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition. Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$). As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will terminate\cite{DBLP:journals/corr/abs-cs-0605132} as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function. More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.

>>>>

In this scenario we consider multiple communities owned by multiple master web services each providing independent request pools. Identical to first scenario master web services form coalitions with web services. We use coalition structure formation methods to partition web services into non-empty disjoint coalition structures. As mentioned in section \ref{sec:coalition} these algorithms \cite{Sandholm1999209, DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve key fundamental problems of what coalitions to form, and how to devide the payoffs from collabration.

@@

The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.

In coalition-formation games, formation of the coalitions is the most important aspect of the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible number of partitions of a set $N$ grows exponentially with the number of players in $n$ (Bell number), and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer a distributed algorithm where each community master and web service can be a decision maker and decide for its own good. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalition to partitions which are preferred by all players inside those coalitions.

This merge-and-split algorithm is designed to be adoptable for different applications. It requires two functions to be specified, first a preference relation for comparing two collections of different coalition partitions of same set of players and second function is to assess the stability condition of a partition. Having two partition sets of players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player improves its payoff in new allocation and all other players maintain their payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$).

In this scenario, as new web services are discovered and get ready to join communities, our algorithm keeps merging and splitting partitions based on the preference function. The decision to merge or split is tied to the fact that all players must benefit, the new web services will merge with communities if $all$ players are able to improve their individual payoff, and some web services may split from old communities, if splitting does not decrease payoff of any web services of the community. According to \cite{DBLP:journals/corr/abs-cs-0605132} this sequence of merging and spliting will converge to a final partition, where players (web services) cannot improve their payoff. More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.
